\bf Supplementary Material to\\ ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''

### 2025-10-04 manuscript/supplement.tex
described investigation in reply letter
style cleaning

\title{\bf Supplementary Material}
\if0\blind
{
  \author[1,2]{Mathew Chandy}
  \author[1]{Elizabeth D. Schifano}
  \author[1]{Jun Yan\thanks{
    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}}
  \author[3]{Xianyang Zhang$^{\ast}$ }
  \affil[1]{Department of Statistics, University of Connecticut}
  \affil[2]{Department of Statistics and Data Science, University of California, Los Angeles}
  \affil[3]{Department of Statistics, Texas A\&M University}
  \maketitle
} \fi

@@

\section{Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration}

@@

\section{Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness} Bias Correction}

@@

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/normal_C_n}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
  \label{fig:qq_n_C_n}
    \hspace{3cm}
  \includegraphics[width = .9\textwidth]{figures/gamma_C_n}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data generating distribution
    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
  \label{fig:qq_g_C_n}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr_C_n}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
    we tested for the gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the normal family.
  }
  \label{fig:rr_C_n}
\end{figure}

Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term.

>>>>

\title{\bf Supplementary Material to\\
  ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''
}
\if0\blind
{
  \author[1,2]{Mathew Chandy}
  \author[1]{Elizabeth D. Schifano}
  \author[1]{Jun Yan\thanks{
    The authors gratefully acknowledge the National Science Foundation (NSF).}\hspace{.2cm}}
  \author[3]{Xianyang Zhang$^{\ast}$ }
  \affil[1]{Department of Statistics, University of Connecticut}
  \affil[2]{Department of Statistics and Data Science, University of California, Los Angeles}
  \affil[3]{Department of Statistics, Texas A\&M University}
  \maketitle
} \fi

@@

\section{Block Size Selection}

@@

\section{Comparison of Two Bias Corrections}

@@

\begin{figure}[tbp]
  %\includegraphics[width = .9\textwidth]{figures/normal_C_n}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
  \label{fig:qq_n_C_n}
    \hspace{3cm}
  %\includegraphics[width = .9\textwidth]{figures/gamma_C_n}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data generating distribution
    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
  \label{fig:qq_g_C_n}
\end{figure}

\begin{figure}[tbp]
  \centering
  %\includegraphics[scale=1]{figures/rr_C_n}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
    we tested for the gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the normal family.
  }
  \label{fig:rr_C_n}
\end{figure}

Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....
